Time Series Modeling of Varying Complexity Captures Subdiffusive Solute Dynamics and Predicts Long Timescale Behavior in Nanoscale Pores.

### 2019-11-22 Ben_Manuscripts/stochastic_transport/Draft.tex
Adjusting visualizations

  \subsection{Mean First Passage Time}

@@

  \subsection{Predicting solute flux}\label{section:mfpt}

  In this section, we use our most promising models to predict solute flux 
  through a theoretical 50 nm channel. For our comparisons to MD, using a truncated
  power law distribution is an obvious choice. However, given that extremely
  long dwells are a rare event, it is possible that studying a much larger set of 
  solutes will fill in the tail of the pure power law PDF. Regarding hop length 
  distributions, the generality of L\'evy stable distributions is powerful, but the
  lack of exact methods for simulation of fractional L\'evy motion reduces it's 
  accuracy and computational tractability. Treating the dynamics as fractional 
  Brownian motion is probably sufficient unless the L\'evy index, $\alpha_h$, is 
  well below 2.

  Choosing which model to use for long timescale projections is not entirely obvious
  without experimental data to compare with.

@@

  \section*{Acknowledgments}
  %MRS: add people who contributed non-author level ideas. 
  %MRS3: add specific info for PRF and GAANN
  %BJC3: I don't know the PRF info. I wrote GAANN as I did on the last paper which is what Rob Davis told me to do
  %MRS4: I willō track down the PRF grant number (if typical)
  This work was supported in part by the ACS Petroleum Research Fund grant XXXXXX 
  and the Graduate Assistance in Areas of National Need (GAANN)
  fellowship which is funded by the U.S. Department of Education.
  Molecular simulations were performed using the Extreme Science and
  Engineering Discovery Environment (XSEDE), which is supported by National
  Science Foundation grant number ACI-1548562. Specifically, it used the Bridges
  system, which is supported by NSF award number ACI-1445606, at the Pittsburgh
  Supercomputing Center (PSC). This work also utilized the RMACC Summit supercomputer,
  which is supported by the National Science Foundation (awards ACI-1532235 and
  ACI-1532236), the University of Colorado Boulder, and Colorado State
  University. The Summit supercomputer is a joint effort of the University of
  Colorado Boulder and Colorado State University.

>>>>

  \subsection{Mean First Passage Time}\label{method:mfpt}

@@

  \subsection{Solute Mean First Passage Times}\label{section:mfpt}

  We used the 1-mode sFBMcut (see Table~\ref{table:anomalous_models}) anomalous 
  diffusion model in order to demonstrate how one can use its realizations in
  order to calculate the MFPT (section~\ref{method:mfpt}) of solutes given model 
  parameters extracted from MD simulations. Any approach which allows one to 
  generate realizations of solute trajectories can be used in place of the AD model.

  In Figure~\ref{fig:mfpt_curves_regular} we show that the MFPT grows super-linearly
  with pore length. We fit a curve of the form $cL^{\alpha}$ to the curves in order
  to estimate the growth exponent, $\alpha$. The growth exponent is inversely proportional
  to the solute MSDs which is consistent with longer passage times for solutes that
  progres through the pores more slowly.

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{mfpt_curves.pdf}
  \caption{}\label{fig:mfpt_curves_regular}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{mfpt_curves_brownian.pdf}
  \caption{}\label{fig:mfpt_curves_brownian}
  \end{subfigure}
  \caption{}\label{fig:mfpt_curves}
  \end{figure}

  The growth exponent is inversely related to the hurst parameter. In 
  Figure~\ref{fig:mfpt_curves_brownian}, we removed the correlation structure (set
  $H$=0.5) from AD trajectory realizations so that all hops were uncorrelated.
  Regardless of the parameters of the dwell time distribution, the growth 
  exponent is always about 2, the same value that we observe for Brownian 
  motion (see Figure~\ref{S-fig:mfpt_curve_brownian} of the Supporting 
  Information).

  Comparison of Figures~\ref{fig:mfpt_curves_regular} and~\ref{fig:mfpt_curves_brownian}
  highlights that the Hurst parameter plays a major role in

  The correlation between hops signficantly

  %BJC: can make design suggestions by trying to decrease anticorrelation by x

%  In this section, we use our most promising models to predict solute flux 
%  through a theoretical 50 nm channel. For our comparisons to MD, using a truncated
%  power law distribution is an obvious choice. However, given that extremely
%  long dwells are a rare event, it is possible that studying a much larger set of 
%  solutes will fill in the tail of the pure power law PDF. Regarding hop length 
%  distributions, the generality of L\'evy stable distributions is powerful, but the
%  lack of exact methods for simulation of fractional L\'evy motion reduces it's 
%  accuracy and computational tractability. Treating the dynamics as fractional 
%  Brownian motion is probably sufficient unless the L\'evy index, $\alpha_h$, is 
%  well below 2.
%  
%  Choosing which model to use for long timescale projections is not entirely obvious
%  without experimental data to compare with.

@@

  \section*{Acknowledgments}
  %MRS: add people who contributed non-author level ideas. 
  %MRS3: add specific info for PRF and GAANN
  %BJC3: I don't know the PRF info. I wrote GAANN as I did on the last paper which is what Rob Davis told me to do
  %MRS4: I willō track down the PRF grant number (if typical)
  This work was supported in part by the ACS Petroleum Research Fund grant \#59814-ND7
  and the Graduate Assistance in Areas of National Need (GAANN)
  fellowship which is funded by the U.S. Department of Education.
  Molecular simulations were performed using the Extreme Science and
  Engineering Discovery Environment (XSEDE), which is supported by National
  Science Foundation grant number ACI-1548562. Specifically, it used the Bridges
  system, which is supported by NSF award number ACI-1445606, at the Pittsburgh
  Supercomputing Center (PSC). This work also utilized the RMACC Summit supercomputer,
  which is supported by the National Science Foundation (awards ACI-1532235 and
  ACI-1532236), the University of Colorado Boulder, and Colorado State
  University. The Summit supercomputer is a joint effort of the University of
  Colorado Boulder and Colorado State University.
